Routines and Regret: An Examination of Behavioral Norms and Emotional Responses

### 2024-02-15 paper/paper.qmd
modify

# load our dataset
data <- read.csv(here::here("data/analysis_data/osf-past-normality-regret-replication-exp1-data.csv"), header = TRUE, stringsAsFactors = FALSE, fileEncoding = "UTF-8-BOM")

>>>>

# load our dataset
data <- read.csv(here::here("data/raw_data/osf-past-normality-regret-replication-exp1-data.csv"), header = TRUE, stringsAsFactors = FALSE, fileEncoding = "UTF-8-BOM")
